ShrinkNets: Learning Network Size while Training

### 2018-02-09 paper/ICML/introduction.tex
changed speedup number

\begin{compactenum}

\item We propose a novel technique based on dynamically switching on and off neurons, 
which allows us to optimize the network size while the network is trained.

\item We implement our technique so as to remove entire neurons, therefore
leading not only to small and well-performing networks, but also dense, which
means higher inference performance. Furthermore, our switching layers used during training can be 
savely removed before the model is used for inference, leading to zero additional overhead.

@@

\item We show that our technique is a relaxation of group LASSO~\cite{Yuan2006}
and prove that our problem admits many global minima.

\item We demonstrate our claims with both fully-connected and convolutional well
known neural network architectures. We show that with ShrinkNets for
\texttt{CIFAR10} we achieve the same accuracy than a traditionally trained
network while reducing the network size by a factor of $2.2x$. Further, when
willing to sacrifice only $1$\% of performance, ShrinkNets finds networks which
are 35\% smaller. All in all, this leads to speedups in inference time of up to
40X.

%\item We demonstrate the efficacy of our technique on both convolutional and
%fully-connected neural nets, showing that ShrinkNets finds networks within
%+/-X\% of best hand-crafted accuracy in XX\% of training time compared to
%existing hyperparameter optimization methods. \srm{Mention the specific
%model/dataset where this is true.}

%\item We demonstrate that ShrinkNets can achieve this accuracy with only YY\% of
%neurons. \srm{This claim should be something about how much smaller a network
%with say 99\% accuracy is one some real dataset}
%
%\item \srm{Some claim about inference time}
%
%\item \srm{Some claim about model size vs performance}

\end{compactenum}

% The remaining of this paper is organized as follows. In section
% \ref{sec:relatedwork} we discuss the related work. In section
% \ref{sec:approach}, we introduce our approach ShrinkNets, followed by the
% practical considerations we implemented to make it work in section
% \ref{sec:impl}. Then, we evaluate the approach in section \ref{sec:evaluation}
% and conclude the paper in section \ref{sec:conclusions}.

>>>>

%\begin{compactenum}

%\item 
\noindent\textbf{1.} We propose a novel technique based on dynamically switching
on and off neurons, which allows us to optimize the network size while the
network is trained.

\noindent\textbf{2.} We implement our technique so as to remove entire neurons,
therefore leading not only to small and well-performing networks, but also
dense, which means higher inference performance. Furthermore, our switching
layers used during training can be savely removed before the model is used for
inference, leading to zero additional overhead.

@@

\noindent\textbf{3.} We show that our technique is a relaxation of group
LASSO~\cite{Yuan2006} and prove that our problem admits many global minima.

\noindent\textbf{4.} We evaluate ShrinkNets with both fully-connected as well as
convolutional neural networks. For \texttt{CIFAR10}, we achieve the same
accuracy than a traditionally trained network while reducing the network size by
a factor of $2.2x$. Further, when willing to sacrifice only $1$\% of
performance, ShrinkNets finds networks which are 35\% smaller. All in all, this
leads to speedups in inference time of up to 6x.

%\end{compactenum}
